%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=.87]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\firstname{HAMDAAN} % Your first name
\familyname{AHMAD} % Your last name

% All information in this block is optional, comment out any lines you don't need

%\address{B Block,Sector 62}{Noida, UP}
\mobile{+91- 7355978830}
\email{ahmadhamdan041@gmail.com}
%\homepage{www.linkedin.com/in/mohitagakhar}{LinkedIn Profile} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
 % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace{-12mm}
{\textnormal{Results-oriented marketing professional with outstanding instincts, innovative spirit, strong leadership, and deep commitment to brand growth across digital channels.}}

\vspace{1mm}
\section{Education}
\cventry{2020--2024}{KIET Group Of Institutions, Delhi-NCR}{B.Tech}{}{\textit{Computer science and engineering}}{}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------
\vspace{-2mm}
\section{Technical Skills}
\cvitem{Coding \& Tools}{\textnormal{C++, SQL, MS Office, Excel, Figma, Google Analytics, Google Search Console, MailChimp, HubSpot, WordPress, Shopify, Adobe Creative Suite, Canva}}

%----------------------------------------------------------------------------------------
%	Masters SECTION
%----------------------------------------------------------------------------------------

%\section{Masters Thesis}

%\cvitem{Title}{\emph{Technologies and characterization of ferroelectric polymers for biomedical sensors}}
%\cvitem{Supervisors}{Professor Antonino Fiorillo}
%\cvitem{Description}{This thesis is based on the implementation of a temperature sensor.}
\vspace{-2mm}
\section{Work Experience}

\cventry{August 2023 -- October 2023}{Social Media Marketing Internship}{\textsc{Techuplabs}}{}{Remote}{
    \begin{itemize}
        \item Created compelling and visually appealing content for various social media platforms, including Facebook, Twitter, Instagram, and LinkedIn.
        \item Utilized social media analytics tools to track key performance metrics, analyze user behavior, and generate detailed reports.
        \item Stayed abreast of the latest social media trends, algorithms, and best practices to optimize content engagement.
        \item Collaborated closely with the marketing team, ensuring alignment of social media efforts with overall marketing strategies.
    \end{itemize}
}


\vspace{1mm}
\cventry{March 2023 -- August 2023}{Graphics Designer}{\textsc{Programming Pathshala}}{}{New Delhi}{
    \begin{itemize}
        \item Developed visually appealing and effective graphic designs for various marketing materials, including websites, social media posts, email campaigns, and print collateral.
        \item Designed visually striking graphics for blog posts, enhancing content's visual appeal and shareability.
        \item Maintained consistency in design elements across all digital platforms, ensuring a cohesive brand identity.
        \item Stayed updated with the latest design trends and emerging technologies to incorporate innovative solutions.
    \end{itemize}
}

\vspace{1mm}
\cventry{June 2021 -- Present}{President and Former Marketing Head}{\textsc{TEDxKIET}}{}{Delhi-NCR}{
    \begin{itemize}
        \item Led a dynamic team in organizing TED events, overseeing all aspects from conceptualization to execution.
        \item Implemented strategic planning and coordinated diverse tasks to ensure seamless event experiences for attendees, speakers, and sponsors.
        \item Developed compelling content for TEDxKIET's digital platforms, including website, social media, and promotional materials.
        \item Negotiated partnerships and sponsorship deals, ensuring mutual benefits and long-term collaborations.
        \item Managed event budgets effectively, optimizing resources and ensuring cost efficiency.
    \end{itemize}
}
\vspace{1mm}
\cventry{January 2023 }{Organizing Member, RANN 23 - Inter college sports fest}{\textsc{KIET}}{}{}{%
    \begin{itemize}
        \item Created visually appealing graphics for the event, including posters, banners, and promotional materials, enhancing the fest's visual identity and appeal.
        \item Successfully marketed RANN 23 on social media platforms, crafting engaging content and leveraging digital marketing strategies to maximize event reach and participation.
        \item Negotiated with sponsors and partners, securing valuable collaborations to support the financial needs.
        \item Collaborated closely with team members to coordinate sporting events, manage registrations, and provide exceptional support to participants and attendees.
    \end{itemize}
}


\vspace{-1mm}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Extra Curricular}
\vspace{-1mm}
\cventry{October 2023}{Designed}{-- striking posters for the Drama Club at Jamia Millia Islamia}{}{}{}
\vspace{-1mm}
\cventry{August 2023}{Freelancing}{--designed compelling thumbnails for a prominent YouTube channel}{}{}{}
\vspace{-1mm}
\cventry{August 2022}{Volunteered}{-- in the International Education awareness week by IRPR KIET in sponsorship}{}{}{}
\vspace{-1mm}
\cventry{June 2022}{Inter-hostel}{-- 1st runner up in Badminton, 2nd runner up Table Tennis}{}{}{}
\vspace{-1mm}
\cventry{May 2022}{Volunteered}{-- in the Blood Donation Camp by Uddeshya Club}{}{}{}
\vspace{-1mm}
\cventry{March 2022}{Meme-a-Thon by Cuvette}{-- 2nd finish  on the leaderboard}{}{}{}
\vspace{-1mm}
\cventry{2021-23}{Conducted}{-- 3 Grand TED events in our college, including TEDxWOMEN}{}{}{}
\vspace{-1mm}
\cventry{Jan-2017}{NCC 'A' certiifed}{-- Got best group dance award among 50 institutes in the summer camp training}{}{}{}
\vspace{-1mm}
%\cventry{2017-19}{Hostel maintenance}{--member of hostel maintenance committee in Gym room and mess}{}{}{}
%\section{Communication Skills}

%\cvitem{2010}{Oral Presentation at the California Business Conference}
%\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \section{Interests}

% \renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
% \cvlistdoubleitem{Piano}{}
% \cvlistitem{Baseball}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}



