
\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small }\\
    \end{tabular*}\vspace{-7pt}
    

}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Hamdaan Ahmad} \\ \vspace{1pt}
    Lucknow, Uttar Pradesh \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 7355978830 ~ \href{mailto:aviralji4@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ahmadhamdan041@gmail.com}} ~
    \href{https://github.com/githamdaan25}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/githamdaan25}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KIET Group of Institutions}{Sept 2020 - Present}
      {Bachelor of Technology in Computer Science and Engineering (76\%)}{Ghaziabad, Uttar Pradesh, India}
  \resumeSubHeadingListEnd
  \vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bright way inter college}{2018 - 2019}
      {Senior Secondary (86.4\%)}{Lucknow, India}
  \resumeSubHeadingListEnd
  \vspace{-11pt}
    

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
          {Infosys - Springboard}{July 2023 -- August 2023}
          {Summer Training on Artificial Intelligence }{Remote}
          \resumeItemListStart
            \resumeItem{Completed an intensive AI training program at Infosys, specializing in machine learning algorithms}
            \resumeItem{Proficient in data preprocessing, feature engineering, and model evaluation techniques through hands-on AI training}
             \resumeItem{Explored cutting-edge AI applications, exhibiting a fervent interest in advancements shaping the field of Research}
        \resumeItemListEnd
  
    \resumeSubheading
      {Feedspace - Techup Labs}{August 2023 -- Present}
      {Digital Media Strategist}{Remote}
      \resumeItemListStart
      \resumeItem{Aligned social media plans with overall business goals and adapted strategies based on performance analytics.}
        \resumeItem{Prioritized and managed Feedspace's Twitter account, curating engaging daily content and fostering audience interactions.}
        \resumeItem{Collaborated with cross-functional teams, including designers, developers, using Figma as the primary tool for product design collaboration on the social media front.}
        \resumeItem{Created social media graphics, on-trend memes, effectively enhancing Feedspace's brand visibility driving higher engagement.}
        \resumeItem{Fostered and nurtured online communities, responding to comments, messages, and inquiries in a timely and engaging manner.}
        
    \resumeItemListEnd
\vspace{-10pt}
    \resumeSubheading
      {TEDxKIET}{July 2021 -- Present}
      {President  and former Marketing head}{Ghaziabad, India}
      \resumeItemListStart
      \resumeItem{Developed and implemented comprehensive event plans, outlining timelines, and resource requirements for the events.}
        \resumeItem{Led cross-functional teams, fostering collaboration and ensuring alignment with project goals and objectives.}
        \resumeItem{Organized and managed three TED events with more than 500 audiences in each of the events}
        \resumeItem{ Managed budgets and resources, optimizing marketing efforts to achieve maximum impact within allocated resources.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Freelance Graphic Designer}{Apr 2021 -- present}
      {Adobe Creative Suite}{Remote}
      \resumeItemListStart
        \resumeItem{Creative Freelance Graphic Designer in developing engaging and innovative digital designs}
        \resumeItem{Managed multiple freelance design projects concurrently, coordinating timelines, deliverables, and client expectations.}
        \resumeItem{Adapted design concepts based on client feedback, demonstrating flexibility and a commitment to client satisfaction.}
    \resumeItemListEnd
    
    
    % \resumeSubheading
    %   {Ek Prayas}{ Dec 2021 -- Present}
    %   {Coordinator}{Ghaziabad, India}
    %   \resumeItemListStart
    %     \resumeItem{Ek Prayas is a social welfare club aimed towards spreading awareness about and eradication of smoking/drinking/drugs used by youth.}
    % \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-6pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Personal Portfolio website} $|$ \emph{HTML, CSS, JS} }{temp}
          \resumeItemListStart
            \resumeItem{Created a responsive, visually appealing portfolio website showcasing tech skills and projects}
            \resumeItem{Responsive, cross-browser compatible design for optimal user experience.}
 \resumeItem{Sections highlighting projects, skills, education, and experience}
          \resumeItemListEnd
    \vspace{-18pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Memory Retention Tool} $|$ \emph{HTML, CSS, JS} }{temp}
          \resumeItemListStart
            \resumeItem{Developed an engaging web-based memory retention tool, Memory Mastermind.}
 \resumeItem{Designed intuitive UI to deliver a seamless gaming experience, promoting brain exercise and cognitive improvement.}
          \resumeItemListEnd

    \vspace{-9pt}
      \resumeProjectHeading
          {\textbf{Feedspace mobile screen} $|$ \emph{Figma}  }{temp}
          \resumeItemListStart
            \resumeItem{Actively contributed in enhancing Feedspace's mobile screens, to deliver a more intuitive and responsive user experience.}
            \resumeItem{Researched and designed impactful enhancements resulting in elevated user engagement and satisfaction.}
            \resumeItem{Played a pivotal role in refining FeedSpace's mobile interface}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------Achievements-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeItemListStart
        \resumeItem{Got an \textbf{internship offer} from \textbf{PCS Management Consultancy Private Limited} for \textbf{Web Developer} role}
        \resumeItem{Conducted \textbf{3 Grand} TED events in our college, including TEDxWOMEN.}
        \resumeItem{Volunteered at Delhi-NCR largest sports fest \textbf{Rann '23} in the Design and Sponsor team} 
        \resumeItem{Volunteered at \textbf{GDG  devfest} in the Design and administration team} 
        \resumeItem{\textbf{2nd finish } on the leaderboardof the meme-a-thon by \textbf{Cuvette}.}
        \resumeItem{Got AWS certification \textbf{Cloud Essentials} on Cloud Computing from Amazon web services}
        % \resumeItem{Involved in student developer communities like \textbf{MLH (Major League Hacking)} and \textbf{Community Classroom}.}
      \resumeItemListEnd
 \end{itemize}
 \vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Skills}{: Project Management, Data Analysis
, Product Roadmapping, User Experience Design(UX), User Interface Design(UI), Product Performance Tracking, Business Analysis, Market Research and Analysis
, graphics designing, }\\
     \textbf{Languages}{: C++, Python, JavaScript, HTML/CSS, SQL} \\
     \textbf{Frameworks}{:  BootStrap  } \\
     \textbf{Developer Tools}{: Git, Power Bi, JIRA, Amplitude, Product plan, , Visual Studio Code, Figma, Adobe Photoshop, Canva, IntelliJ, Github, Behance, Dribble} \\
     \textbf{Libraries}{: pandas, NumPy, } \\
     % \textbf{Theoretical Concepts}{: Data Structures and Algorithms, DMBS, Operating System, Computer Networks } \\
    }}
 \end{itemize}
 \vspace{-16pt}

 
% %
% %-----------Miscellaneous-----------
% \section{Miscellaneous}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      {Consider myself to be a \textbf{teamworker}.} \\
%      {Proficient in English and Hindi.} \\
%      {\textbf{Hobbies:} Solving CTFs, Sketching, Cooking.} \\
%     }}
%  \end{itemize}
%  \vspace{-16pt}

\end{document}
